Multi-channel Kondo model URG

### 2022-01-12 combined_manuscript/other/send_abhirup/MultiChannelKondo_manuscript.tex
combined manuscripts, separated into main and supplementary, changed Kondo coupling to curly J

\section{Stargraph and its properties}
\subsection{Hamiltonian and wavefunctions}
\noindent As shown in the previous section, at the heart of multi channel Kondo there is a stargraph problem whic is the zero mode of the lowenergy fixed point Hamiltonian of the Multi channel Kondo. In this section our focus will be on the stargraph problem itself.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.4]{plt/stargraph_first}
\caption{This is a stargraph model with one central spin $\vec{S}_d$ and $K$ outer spin $1/2$s. The central spin is coupled with all the outer spins with Heisenberg coupling with coupling strength $\alpha$.}
\label{fig:stargraph_first}
\end{figure}
As shown in the Fig.\ref{fig:stargraph_first} above one central spin ($\vec{S}_d$) is connected with $K$ spins forming a $K$ channel stargraph problem corresponding to the $K$-channel Kondo problem. The Hamiltonian of this above model is given as 
\begin{eqnarray}
H &=& \alpha \vec{S}_d.\sum_{i=1}^{K}\vec{S}_i=\alpha \vec{S}_d.\vec{S} \nonumber\\
&=& \frac{\alpha}{2} (\vec{J}^2-\vec{S}^2-\vec{S}_d^2)~,~~\alpha >0.
\label{eq:stargraph_hamiltonian}
\end{eqnarray}
where $\vec{J}=\vec{S}+\vec{S}_d$ and $\vec{S}=\sum_{i=1}^{K} \vec{S}_i$. One can see that the large psin $S$ can take many possible values as this is made out of $K$ spin 1/2s. We can see $[H,J]=0=[H,J^i]$ for  $i=x,y,z$, $[J^i,J^j]\neq 0$ for $i\neq j$. Also the operators $\hat{Z}=2^{K+1}S_d^z\prod_{i=1}^{K} S_i^z $ and $\hat{X}=2^{K+1}S_d^x\prod_{i=1}^{K} S_i^x $ commutes with the Hamiltonian, $[H,\hat{Z}]=0=[H,\hat{X}]$ though $[\hat{Z},\hat{X}]\neq 0$, in general.
 Thus we can form the CSCO with $H,J,J^z,S,S_d$. For a particular value $S$, $J$ can take two values $S\pm S_d$ with the energies $-\alpha S_d(S_d+1\mp J)$ respectively. $S_d$ is fixed thus the energy values only depends on the corresponding $J$ value of the state. As the energy does not depends on the $J^z$, all $2J+1$ $J^z$ states labeled by $|S_d,S;J,J^z\rangle$ are degenerate. It is easy to see that the ground state has energy $E=-\alpha S_d(S_d+1+J)$ with  $J=S-S_d$, thus $E_g=-\alpha S_d(S_{max}+1)$ with $S$ taking the maximum possible value $S_{max}=K/2$.

\subsubsection{Ground state wavefunction}
\noindent Above calculations show stargraph with $K$ channels has $K$-fold ground state degeneracy, states labeled as $|S_d,S;J,J^z\rangle$ where $J^z$ takes $K=2J+1$ distinct values, $J^z=\{-J,\cdots,+J \}$. Here our goal is to find the wavefunction in the fundamental spin basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$. To achieve that we use the Clebsch-gordon coefficients, we know for two spins $j_1$ and $j_2$  with total spin $J$ and $J^z=M$ one can expand the state as 
\begin{eqnarray}
|j_1,j_2;J,M\rangle &=& \displaystyle\sum_{\substack{m_1=\{-j_1,\cdots,j_1\} \\ m_2=\{-j_2,\cdots,j_2\} }}   \mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M} |j_1,m_1;j_2,m_2 \rangle ,~~~~
\end{eqnarray}
where $j_1^z=m_1$ and $j_2^z=m_2$ and $\mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M}$ is the Clebs-Gordon coefficient. In our problem two spins $S_d$ and $S$ are forming one large spin $J$ represented by the state $|S_d,S;J,J^z\rangle$, in the ground state $J=S-1/2$. Thus the ground state $|S_d,S; (S-\frac{1}{2} ),M\rangle \equiv |\alpha\rangle$ can be expanded as
%{%\tiny
\begin{eqnarray}
%&&\bigg|S_d,S;\bigg(S-\frac{1}{2}\bigg),M\bigg\rangle = ww\\
&&|\alpha\rangle= \displaystyle\sum_{\substack{m_1=\{-S_d,\cdots,S_d\} \\ m_2=\{-S,\cdots,S\} }} \mathcal{C}^{S_d,m_1;S,m_2}_{S_d,S;J,M} ~~   | S_d,m_1 \rangle \otimes  |S,m_2  \rangle ,~~~~
\end{eqnarray}
%}
Because in the ground state $S$ is maximum, the state $|S,S^z\rangle$ can be decomposed in terms of a two spin problem of spin $1/2$ and $S-1/2$ forming the state $|1/2,S-1/2;S,S^z\rangle$ which can be further expanded in the basis $ |1/2,m'_1 \rangle \otimes  |S-1/2,m'_2  \rangle $ where $m'_1,m'_2$ are the z-components of the spin $1/2$ and $S-1/2$. Next we decompose the state $|S-1/2,m'_2\rangle$ in further smaller spin problem and so on. This way we finally arrive at the ground state wavefunction in terms of the fundamental basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$, give as
\begin{eqnarray}
|S_d,S;J,M\rangle &=& \sum_{S_d^z,\{S_i^z\}} \mathcal{D}_{S_d^z,\{S_i^z\}} |S_d^z,S_1^z,\cdots,S_K^z\rangle
\label{eq:wf_fundamental_basis}
\end{eqnarray}
where $\{S_i^z\}\equiv(S_1^z,\cdots,S_K^z)$ and the coefficient $\mathcal{D}_{S_d^z,\{S_i^z\}}$ is given as 
\begin{eqnarray}
\mathcal{D}_{S_d^z,\{S_i^z\}}  &=& \displaystyle\sum_{\substack{m_2=[-S,S]\\ m_4=[-(S-1/2),(S-1/2)]\\~.~\\  m_{2N-4}=[-1,1]   }} \mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~ ,m_{2N-2}}~,~~~~~~
\end{eqnarray}
and further the coefficients $\mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~, m_{2N-2}} \equiv\Sigma$, are made out of the products of Clebsh-Gordon Coefficients
\begin{eqnarray}
%\mathcal{M}^{\{m^{(1)}\}}_{\{m^{(2)}\}} &=& 
\Sigma=\mathcal{C}^{S_d,S_d^z;S,m_2}_{S_d,S;J,M} ~~ \mathcal{C}^{S_1,S_1^z;(S-1/2),m_4}_{S_1,(S-1/2);S,m_2} \cdots  \mathcal{C}^{S_{K-1},S_{K-1}^z;S_K,S_K^z}_{S_{K-1},S_{K};1,m_{2N-4}}~,~~~~
\end{eqnarray}
Using these wavefunctions we can calculate various entanglement features of this stargraph problem.

@@

\subsubsection{Impurity entanglement entropy}
\begin{figure}[!h]
\centering
\includegraphics[scale=0.32]{plt/EE_multi_channel_ANN.png}
\caption{Caption }
\label{fig:EE_d}
\end{figure}
\noindent Here we are interested in finding the entanglement of the central impurity spin with the rest of the multi-channel bath zero mode. For single channel case the the ground state is unique and is $|J=0,J_z=0 \rangle = \frac{1}{\sqrt{2}} (|\uparrow_{d}\downarrow_0\rangle -|\downarrow_d \uparrow_0\rangle)$. Thus, one can easily calculate the reduced density matrix of the impurity by tracing out the $0^{th}$ state. From that reduced denisty matrix the entanglement entropy is $\log 2$, which is maximum possible for a spin-1/2. In the case of multi-channel problem there are $K$ orthogonal set of ground states $|J^z\rangle$, for each such state the entaglement is different. The state $|J^z\rangle \equiv |S_d=1/2,S=K/2;(S-1/2),J^z\rangle$ can be written in the fundamental basis as shown in the Eq.\eqref{eq:wf_fundamental_basis}. Then the density matrix is $\rho=|J^z\rangle\langle J^z|$ from which we can calculate the reduced density matrix by partial tracing the impurity degree of freedom 
%$\rho_{d}=\textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle$. 
\begin{eqnarray}
\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}
\end{eqnarray}
\noindent The eigenvalues of this reduced density matrix given by $\lambda_i$ is called entanglement spectrum. We are interested in the von-Neumann entanglement entropy of the impurity spin with thte rest ($EE_d$). We are intersted in the scaling of this entanglement entropy with the channel number. As shown in the Fig.\ref{fig:EE_d} the x-axis is the channel number and for a particular channel there are may possible entanglement values corresponding to different $J^z$ states. The minimum entanglement entropy state (associated with the $J^z=J$ state) decreases show the classical nature of this maximally polarized state. On the other hand the maximum entanglement entropy (associated with $J^z_{min}$ state) for a particular channel $K$ is saturating to $\log K$ in the large $K$ limit. Another important result that we see, for any odd value of $K$ the minimum entanglement entropy associated with $J^z=0$ is $\log 2$ shows a formation of perfectly entangled state made out of more than 2 spins (e.g; singlet). In this state $|J^z=0\rangle$ all the $K$(odd) outer spins participate in quantum scattering with the central impurity spin in such a way the central spin is maximally entangled which is not the case for any other $J^z$ state. In the large $K$ limit irrespective it's even and odd nature there are always a $J^z_{min}$ state where the central impurity spin is maximally entangled.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.32]{plt/outer_EE_multi_channel_ANN.png}
\caption{caption}
\label{fig:EE_outer}
\end{figure}
In a $K$ channel system all the outer spins are equivalent (has $Z_N$ symmetry), thus studying the entanglement of any one outer spin with the rest is enough. Here we do a similar entanglement entropy study where we get the reduced density matrix ($\rho_o$) by partial tracing out any one outer spin say the $l^{th}$ ($1\leq l \leq K$) one $S^z_{l}$. 
\begin{eqnarray}
\rho_{o} &=& \textrm{Tr}_{l} \rho =\displaystyle\sum_{S^z_{l}} \langle S^z_l | \rho | S^z_{l} \rangle~,~EE_o=-\rho_{o}\log \rho_{o}
\end{eqnarray}
We do a similar entanglement scaling with the channel number $K$. We find that minimum entanglement entropy associated with the state $J^z=J$ is approaching zero in the limit $K\gg 1$. In contrast the minimum entanglement entropy associated with $J^z_{min}$ state is saturating at $\log 2$ in the large $K$. Thus in the state $J^z=0$ for any $K$ (or $J^z=\pm 1/2$ for $K\gg 1$) any outer spin is maximally entangled with the rest.

\par The above entanglement studies Fig.(\ref{fig:EE_d},\ref{fig:EE_outer}) show  that for odd channel case there exist a state $J^z=0$ where the central spin $S_d$ and any outer spin $S_i$ is maximally entangled with the rest. This shows the special and unique property of the stargraph ground state where you can create state made out of morethan 2 spins where each any every one is maximally entangled with the rest. Thus this stargraph ground state is very important in the quantum information theory. 
\textbf{write here}

\subsubsection{Macroscopic singlet state}
\noindent  The $|J^z=0\rangle_{K} $ state of a $K$(odd) channel stargraph problem can be very genrally written as
\begin{eqnarray}
|J^z=0\rangle_K &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow\rangle_d \otimes |\gamma_{\downarrow}\rangle_K -  |\Downarrow\rangle_d \otimes |\gamma_{\uparrow}\rangle_K \bigg]  
\label{eq:maximally_entangled_state}
\end{eqnarray}
where $|\Uparrow\rangle_d$ and $|\Downarrow\rangle_d$ represents the impurity state $S_d^z=\pm 1/2$ respectively. Let's define $U_{+}$ represents the set of all possible sub-systems of the set $[K]$ with $(K+1)/2$ numbers of elements in it. We define complement of any one set $g\in U_+$ , $g^{c}$ such that $g\cup g^{c}=[K]$.
\begin{eqnarray}
|\gamma_{\sigma} \rangle_K &=& \frac{1}{\sqrt{{K \choose \frac{K+1}{2}} }} \displaystyle\sum_{\substack{ g\in U_{+} }} \prod_{\substack{i\in g \\j\in g^c}} |\sigma_i\rangle \otimes |\bar{\sigma}_j \rangle~,~ 
\end{eqnarray}
where $\sigma_i=\pm 1/2$ and $\bar{\sigma}_i=-\sigma_i$, $\pm 1/2$ representing the state $\uparrow_i,\downarrow_i$ respectively for the $i^{th}$ spin. Thus the density matrix for this state $|J^z=0\rangle_K$ can be written as $\rho=|J^z=0\rangle_K \langle J^z=0|_K$. For this state one can simply verify that $\rho_{d}=\textrm{Tr}_d \rho=\frac{1}{2} (|\gamma_{\downarrow}\rangle_K \langle\gamma_{\downarrow}|_K + |\gamma_{\uparrow}\rangle_K \langle\gamma_{\uparrow}|_K)$  which has eigenvalues $1/2,1/2$ leading to the entanglement entropy $S_{d}= \log 2$. Similary one can verify that the entanglement entropy of any other spin with the rest is $\log 2$. Thus all the spins in the state eq.\eqref{eq:maximally_entangled_state} is maximally entangled with the rest representing a macroscopic singlet state with morethan $2$ spins.

@@

\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_0_1}
\caption{ds}
\label{fig:MI_d_o}
\end{figure}
\noindent In the above study our focus was on the von-Neumann entanglement entropy, now we are interested in the correlation signatures present in the stargraph grounds states. Mutual inforamtion is one such measure which captures the correlations present between two subsystems (A,B) in a particular state defined as
\begin{eqnarray}
I^2(A:B)=S_A+S_B-S_{A\cup B}
\end{eqnarray}
where $S_{A}$ is the von-Neumann entanglement entropy of the subsystem $A$ with the rest. Here we are interested in computing two types of mutual inforamtions first, study the mutual information between the impurity-spin and one outer spin $I^2(d:o)$. Because all the outer spins are symmetric, the mutual information between impurity-spin with any one outer spin is same and can capture the correlation between two $A$ and $B$. We have done a scaling study of this mutual information for different channel numbers $K$. As shown in the Fig.\ref{fig:MI_d_o} in the large $K$ limit the maxima of the mutual information associated with the state $J^z_{min}$ is saturating at $1.076$ and the Mutual information associated with the state $J^z=J$ is decreasing showing the classical limit.
\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_1_2}
\caption{ds}
\label{fig:MI_o_o}
\end{figure}
Next, we have done a similar study by calculating the mutual information between two outer spin $I^2(o:o)$. In this also we find that the maximum mutual information between any outer spins saturates at the value $1.076$ similar to the $I^2(d:o)$ case.

\par As can be seen from the above Figure.(\ref{fig:MI_d_o},\ref{fig:MI_o_o}) that  both the maximum mutual information of $I^2(d:o)$ and $I^2(o:o)$ try to saturate near the same value. Thus in the large $K$ limit in the $J^z_{min}$ state mutual information between any two spins in the stargrah model is same saturating at a constant value ($1.076$). Though the difference can be seen in the state $J^z=J$ where the mutual information thus correlation s between two outer spins vanishes in the large $K$ limit faster than the mutual information between the impurity and any one outer spin. Thus correlation wise there is no difference between impurity-outer pair and outer-outer pair in the large $K$ limit.

\subsubsection{Multi-partite information}
\noindent Similar to the mutual inforamtion one can calculate any higher order mutli-partie inforamtion to find the nature of the correlations present in different ground states. We define the tripartite information among three subsystems $A,B,C$ as $I^3_{ABC} = (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~$. This tri-parite information scaling with the number of channels $K$ also shown behavior similar to the mutual information case, the highest tri-partite information is associated with the $J^z_{min}$ state and saturating in the limit of $K\gg 1$. One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}\}\equiv\{A_1,A_2,\cdots,A_K\}$. To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$. We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively. Finally, the von Neumann entanglement entropy of the subsystem $A$ is given by $S_{A} $. Then the $N-$partite information that we are interested in is defined as
\begin{eqnarray}
I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
\label{eq:I_N_definition}
\end{eqnarray}
Studying these mutli-partite informations one can understand the nature of the correlations present among the outer spins.
\begin{figure}
\includegraphics[scale=0.32]{plt/I_N_vs_N_N9.png}
\caption{This figure shows how the $m-partite$ information varies with $m$ showing the entanglement distribution amond different number of outer-spins.}
\label{fig:Im_vs_m}
\end{figure}
\noindent Our study of this multi-partite information presented in the above Fig.\eqref{fig:Im_vs_m} shows that the higher oreder multi partite informations decreaseas as you increase the order folloring a power law. \textbf{Show the fittings.}

>>>>

\section{Stargraph and its properties}
\subsection{Hamiltonian and wavefunctions}
\noindent As shown in the previous section, at the heart of multi channel Kondo there is a stargraph problem whic is the zero mode of the lowenergy fixed point Hamiltonian of the Multi channel Kondo. In this section our focus will be on the stargraph problem itself.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.4]{plt/stargraph_first}
\caption{This is a stargraph model with one central spin $\vec{S}_d$ and $K$ outer spin $1/2$s. The central spin is coupled with all the outer spins with Heisenberg coupling with coupling strength $\alpha$.}
\label{fig:stargraph_first}
\end{figure}
As shown in the Fig.\ref{fig:stargraph_first} above one central spin ($\vec{S}_d$) is connected with $K$ spins forming a $K$ channel stargraph problem corresponding to the $K$-channel Kondo problem. The Hamiltonian of this above model is given as 
\begin{eqnarray}
H &=& \alpha \vec{S}_d.\sum_{i=1}^{K}\vec{S}_i=\alpha \vec{S}_d.\vec{S} \nonumber\\
&=& \frac{\alpha}{2} (\vec{J}^2-\vec{S}^2-\vec{S}_d^2)~,~~\alpha >0.
\end{eqnarray}
where $\vec{J}=\vec{S}+\vec{S}_d$ and $\vec{S}=\sum_{i=1}^{K} \vec{S}_i$. One can see that the large psin $S$ can take many possible values as this is made out of $K$ spin 1/2s. We can see $[H,J]=0=[H,J^i]$ for  $i=x,y,z$, $[J^i,J^j]\neq 0$ for $i\neq j$. Also the operators $\hat{Z}=2^{K+1}S_d^z\prod_{i=1}^{K} S_i^z $ and $\hat{X}=2^{K+1}S_d^x\prod_{i=1}^{K} S_i^x $ commutes with the Hamiltonian, $[H,\hat{Z}]=0=[H,\hat{X}]$ though $[\hat{Z},\hat{X}]\neq 0$, in general.
 Thus we can form the CSCO with $H,J,J^z,S,S_d$. For a particular value $S$, $J$ can take two values $S\pm S_d$ with the energies $-\alpha S_d(S_d+1\mp J)$ respectively. $S_d$ is fixed thus the energy values only depends on the corresponding $J$ value of the state. As the energy does not depends on the $J^z$, all $2J+1$ $J^z$ states labeled by $|S_d,S;J,J^z\rangle$ are degenerate. It is easy to see that the ground state has energy $E=-\alpha S_d(S_d+1+J)$ with  $J=S-S_d$, thus $E_g=-\alpha S_d(S_{max}+1)$ with $S$ taking the maximum possible value $S_{max}=K/2$.

\subsubsection{Ground state wavefunction}
\noindent Above calculations show stargraph with $K$ channels has $K$-fold ground state degeneracy, states labeled as $|S_d,S;J,J^z\rangle$ where $J^z$ takes $K=2J+1$ distinct values, $J^z=\{-J,\cdots,+J \}$. Here our goal is to find the wavefunction in the fundamental spin basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$. To achieve that we use the Clebsch-gordon coefficients, we know for two spins $j_1$ and $j_2$  with total spin $J$ and $J^z=M$ one can expand the state as 
\begin{eqnarray}
|j_1,j_2;J,M\rangle &=& \displaystyle\sum_{\substack{m_1=\{-j_1,\cdots,j_1\} \\ m_2=\{-j_2,\cdots,j_2\} }}   \mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M} |j_1,m_1;j_2,m_2 \rangle ,~~~~
\end{eqnarray}
where $j_1^z=m_1$ and $j_2^z=m_2$ and $\mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M}$ is the Clebs-Gordon coefficient. In our problem two spins $S_d$ and $S$ are forming one large spin $J$ represented by the state $|S_d,S;J,J^z\rangle$, in the ground state $J=S-1/2$. Thus the ground state $|S_d,S; (S-\frac{1}{2} ),M\rangle \equiv |\alpha\rangle$ can be expanded as
%{%\tiny
\begin{eqnarray}
%&&\bigg|S_d,S;\bigg(S-\frac{1}{2}\bigg),M\bigg\rangle = ww\\
&&|\alpha\rangle= \displaystyle\sum_{\substack{m_1=\{-S_d,\cdots,S_d\} \\ m_2=\{-S,\cdots,S\} }} \mathcal{C}^{S_d,m_1;S,m_2}_{S_d,S;J,M} ~~   | S_d,m_1 \rangle \otimes  |S,m_2  \rangle ,~~~~
\end{eqnarray}
%}
Because in the ground state $S$ is maximum, the state $|S,S^z\rangle$ can be decomposed in terms of a two spin problem of spin $1/2$ and $S-1/2$ forming the state $|1/2,S-1/2;S,S^z\rangle$ which can be further expanded in the basis $ |1/2,m'_1 \rangle \otimes  |S-1/2,m'_2  \rangle $ where $m'_1,m'_2$ are the z-components of the spin $1/2$ and $S-1/2$. Next we decompose the state $|S-1/2,m'_2\rangle$ in further smaller spin problem and so on. This way we finally arrive at the ground state wavefunction in terms of the fundamental basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$, give as
\begin{eqnarray}
|S_d,S;J,M\rangle &=& \sum_{S_d^z,\{S_i^z\}} \mathcal{D}_{S_d^z,\{S_i^z\}} |S_d^z,S_1^z,\cdots,S_K^z\rangle
\end{eqnarray}
where $\{S_i^z\}\equiv(S_1^z,\cdots,S_K^z)$ and the coefficient $\mathcal{D}_{S_d^z,\{S_i^z\}}$ is given as 
\begin{eqnarray}
\mathcal{D}_{S_d^z,\{S_i^z\}}  &=& \displaystyle\sum_{\substack{m_2=[-S,S]\\ m_4=[-(S-1/2),(S-1/2)]\\~.~\\  m_{2N-4}=[-1,1]   }} \mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~ ,m_{2N-2}}~,~~~~~~
\end{eqnarray}
and further the coefficients $\mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~, m_{2N-2}} \equiv\Sigma$, are made out of the products of Clebsh-Gordon Coefficients
\begin{eqnarray}
%\mathcal{M}^{\{m^{(1)}\}}_{\{m^{(2)}\}} &=& 
\Sigma=\mathcal{C}^{S_d,S_d^z;S,m_2}_{S_d,S;J,M} ~~ \mathcal{C}^{S_1,S_1^z;(S-1/2),m_4}_{S_1,(S-1/2);S,m_2} \cdots  \mathcal{C}^{S_{K-1},S_{K-1}^z;S_K,S_K^z}_{S_{K-1},S_{K};1,m_{2N-4}}~,~~~~
\end{eqnarray}
Using these wavefunctions we can calculate various entanglement features of this stargraph problem.

@@

\subsubsection{Impurity entanglement entropy}
\noindent Here we are interested in finding the entanglement of the central impurity spin with the rest of the multi-channel bath zero mode. We know that for multi channel case the ground state is degenerate, thus for each degenerate state we can calculate the entanglement entropy. As we have already discussed for $N_{ch}$ number of channels there are $N_{ch}$ number of degenerate ground states, labeled by the $J_z$ quantum number.\\
\par For single channel case the the ground state is unique and is 
\begin{eqnarray}
|J=0,J_z=0 \rangle &=& \frac{1}{\sqrt{2}} (|\uparrow_{d}\downarrow_0\rangle -|\downarrow_d \uparrow_0\rangle)
\end{eqnarray}
Thus, one can easily calculate the reduced density matrix of the impurity by tracing out the $0^{th}$ state. From that reduced denisty matrix the entanglement entropy is $\log 2$, which is maximum possible for a spin-1/2.
\par Next, we are interested in findig this entanglement entropy for the multi-channel case $N_{ch}>1$. We have generated the degenerate ground states analytically using the Clebsch-Gordon coefficients. On this wavefunctions we do various entanglement and correlation studies. We start with the ground state wavefunction, $|\psi_g\rangle_{J_z}=|1/2_{d},S;J,J_z\rangle$, starting with one of those degenerate ground states labeled by $J_z$ we calculate the density matrix.
\begin{eqnarray}
\rho_{J_z}=|\psi_g\rangle_{J_z} \langle\psi_g|_{J_z}
\end{eqnarray}

\begin{figure}[!h]
\centering
\includegraphics[scale=0.32]{plt/EE_multi_channel_ANN.png}
\includegraphics[scale=0.32]{plt/outer_EE_multi_channel_ANN.png}
\caption{Y-axis shows the impurity entanglement entropy with the rest and X-axis shows the number of channels $N_{ch}$. For one value of $N_{ch}>1$, there are $N_{ch}$ degenerate ground states and their corresponding impurity entanglement entropy. }
\end{figure}

\noindent Using the wavefunction we can do the partial tracing on the impurity spin to get the reduced denisty matrix of the rest. From that we get entanglement entropy for different number of channels. For even number of channel cases $J_z$ and $-J_z$ sector has same entanglement entropy. For the case of odd $N_{ch}$ there also $\pm J_z$ sectors shares same entanglement entropy, but there is a state $J_z=0$ which has entanglement entropy $\log 2$. Thus from the above we can see that $J_z=0$ state corresponding to odd number of channels shows perfect screenig interms of the maximum entanglement entropy and $J_z=0$ magnetization.

@@

Mutual information between two sub-systems $A, B$ is defined as, 
\begin{eqnarray}
I^2(A:B)=S_A+S_B-S_{A\cup B}
\end{eqnarray}

\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_0_1}
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_1_2}
\caption{\textit{Left:} Y-axis is the mutual information between the impurity-spin and one outer spin and x-axis is the number of channel $N_{ch}$. \textit{Right:} This shows the variation of mutual inforamtion between two outer spins.}
\label{fig:MI_vs_Nch}
\end{figure}

We first study the mutual information between the impurity-spin and one outer spin $I^2(d:o)$. Because all the outer spins are symmetric, the mutual information between impurity-spin with any one outer spin is same. Next we calculate the mutual information between two outer spin $I^2(o:o)$. One can see that the maximum mutual information for both the cases are from the $(J_z)_{min}$ state. For odd number of channels $(J_z)_{min}=0$ and for even number of channels $\pm (J_z)_{min}=\pm 1/2$. And the minimum mutual information corresponds to the $\pm (J_z)_{max}=\pm J$ state.\\

\par As can be seen from the above Figure.\ref{fig:MI_vs_Nch} that  both the maximum mutual information of $I^2(d:o)$ and $I^2(o:o)$ try to saturate near the same value. Thus in the lowest $J_z$ sector the entanglement distribution between impurity and outer vs outer and outer is same. Which suggests that even though there were no coupling among the outer spins explicitly, there are entanglement among them. The minimum of the mutual information coming from the largest $J_z$ sector, the $I^2(o:o)$ corresponding to this sector asymptotically approach zero for large $N_{ch}$ limit. Which shows that in the large channel limit $N_{ch}\gg 1$ though the $min~I^2(o:o)$ pparoach zero the $min~ I^2(d:o)$

\subsubsection{Tri-partite information}
\noindent Apart from Mutual information we can calculate the tri-partie information also. This tri-partite information is defined among three sub-systems $A,B,C$ , as

\begin{eqnarray}
I^3_{A,B,C} &=& (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~,
\end{eqnarray}

\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_3_vs_Nch_1_2_3}
%\includegraphics[scale=0.32]{plt/I_4_vs_Nch_1_2_3_4}
\caption{This plot shows the variation of the tri-partite information with the number of channels $N_{ch}$.}
\label{fig:I3_vs_Nch}
\end{figure}
\noindent Our tri-partite infrmation measure (Fig.\ref{fig:I3_vs_Nch}) among the outer spins shows that the just like the mutual information the minimum tri-partite information asymptotically approaches zero in the $N_{ch}\gg 1$ limit. Same is the case for 4-partite information also.

\subsubsection{$I_N$ vs N}
\noindent Here we are intersted in understading the entanglement dristribution among different number of outter spins. To find that out we take a multi-channel stargraph model with $N_{ch}$ noumber of outer spins. We calculate different multi partite inforamtions $I^m, m\in \{2,\cdots,N_{ch}\}$ on it's $N_{ch}$ degenerate ground states.

\begin{figure}
\includegraphics[scale=0.32]{plt/I_N_vs_N_N9.png}
\caption{This figure shows how the $m-partite$ information varies with $m$ showing the entanglement distribution amond different number of outer-spins.}
\label{fig:Im_vs_m}
\end{figure}
\noindent Our above study (Fig.\ref{fig:Im_vs_m}) shows that the mutual imformation has the maximum value and higher odere multi-parite informations is smaller and smaller approaching zero.

\subsection{Correlation Studies}

\subsubsection{Quantum energy}
\noindent Here we are interested in the energy expectation value arising from the quantum fluctuation part of the Hamiltonian (\ref{eq:zero_mode}). We define ising enregy $E_{ising}$ and quantum energy $E_{Q}$ in the ground state $|\psi_g\rangle$ as,
\begin{eqnarray}
E_{ising} = |\langle \psi_g | \mathcal{H}^c_0 | \psi_g \rangle| ,~~ E_{Q} &=& |\langle \psi_g | \mathcal{H}^Q_0 | \psi_g \rangle|=|E_g|-|E_{ising}|~, \nonumber\\
&=& \frac{\alpha(S+1)}{2} - |E_{ising}|.
\end{eqnarray}  
This quantum energy $E_Q$ is generated by the spin-flips between the impurity spin and the outer spin. Thus it is interesting to findout how this quantum energy changes with the increase of the number of channels $(N_{ch})$. Another important parameter is the Quantum enrgy per channel, $e_Q=|E_Q|/N_{ch}$, and it's variation towards the infinity channel limit. We know in the gorund state $N_{ch}=2S$ thus,
\begin{eqnarray}
e_Q &=& \frac{\alpha(S+1)}{4S} - \frac{|E_{ising}|}{2S} ~,~\nonumber\\
%&=& \alpha\frac{(N_{ch}+2)}{4N_{ch}}-\frac{|E_{ising}|}{N_{ch}} ~,~ \nonumber\\
%&=& \alpha \bigg(\frac{1}{4} +\frac{1}{2N_{ch}} \bigg)-\frac{|E_{ising}|}{N_{ch}}~,~\nonumber\\
&=& \frac{\alpha}{4} -\frac{1}{N_{ch}} \bigg(|E_{ising}| -\frac{\alpha}{2}  \bigg)~,~
\end{eqnarray}
Thus from the above equation of quantum energy per channel one can see that in the inifinity-channel limit $N_{ch}\rightarrow \infty$,

\begin{eqnarray}
e_Q = \frac{\alpha}{4}- \frac{|E_{ising}|}{N_{ch}} < \frac{\alpha}{4}~,~
\end{eqnarray}

\begin{figure}[!h]
\centering
\includegraphics[scale=0.34]{plt/Quantum_Energy_per_channel}
\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins. }
\end{figure}
